Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-15 WholePlotTrajectories.tex
relecture

A combination of taxonomic and functional approaches are essential to
fully assess communities response to disturbance and differences in
their respective trajectories are insightful of underlying mechanisms
\citep{Lohbeck2015, Guariguata2001}. Although taxonomic and functional
diversity are complementary and sometimes decoupled, they are combined
in the measure of communities functional redundancy that quantifies the
amount of shared trait values among species \citep{Carmona2016}.
Functional redundancy is determinant of communities resilience as high
redundancy, like in highly diverse tropical forests
\citep{Bellwood2006}, mitigates the impacts of species removal on
ecosystem functioning \citep{Trenbath1999, Elmqvist2003, Diaz2005}.

>>>>

A combination of taxonomic and functional approaches are essential to
fully assess communities response to disturbance and the differences in
their trajectories are insightful of assembly processes
\citep{Lohbeck2015, Guariguata2001}. The decoupling between functional
and taxonomic trajectories is assessed through communities functional
redundancy that quantifies the amount of shared trait values among
species \citep{Carmona2016}. Functional redundancy, which is high in the
very diverse tropical forests \citep{Bellwood2006}, mitigates the
impacts of species removal on ecosystem functioning
\citep{Trenbath1999, Elmqvist2003, Diaz2005} and thus determines
communities resilience. High functional redundancy besides increases the
functional overlap among species, increasing their similarity, and would
foster neutral stochastic processes \citep{Gravel2006}.
